---
title: "p8105_hw1_niz2000"
author: "Nora Zakaria"
date: "2019-09-20"
output: github_document
---

# PROBLEM 1

## Create a Data Frame

In order to create a data frame, the tidyverse package must be loaded.

```{r}
library (tidyverse)
```

### The data frame consists of:
* A random sample of size 8 from a standard Normal distribution
* A logical vector indicating whether elements of the sample are greater than 0
* A fruit-themed character vector of length 8
* A factor vector of length 8, with 3 different factor levels: "seed", "pit", and "peel"

```{r}
set.seed(7)

Prob1_df = tibble(
  sample = rnorm(8),
  vec_logical = c(sample > 0), 
  vec_character = c("apple", "banana", "cherry", "date", "elderberry", "fig", "guava", "honeydew"),
  vec_factor = factor(c("seed", "peel", "pit", "pit", "seed", "peel", "seed", "seed"))
)
```

## Mean of Variables in the Data Frame

In this next code chunk, an attempt was made to take the mean of each variable in the dataframe Prob1_df. 

```{r}
mean(pull(Prob1_df, sample))
mean(pull(Prob1_df, vec_logical))
mean(pull(Prob1_df, vec_character))
mean(pull(Prob1_df, vec_factor))
```

The code only displays a result for the mean of the sample and logical vector. It does not display a mean for the character vector or factor vector, as they are not tied to numbers, and therefore you cannot find their mean. 

## Convert Variables

```{r eval = FALSE}
as.numeric(pull(Prob1_df, sample))
as.numeric(pull(Prob1_df, vec_logical))
as.numeric(pull(Prob1_df, vec_character))
as.numeric(pull(Prob1_df, vec_factor))
```

You can only convert the sample, logical, and factor variables from the data frame to numeric variables. The character variable could not be converted to numeric, as it did not consist of numbers or and is not assigned numeric indicies. For that same reason, you can not take the mean of character variables, seen above. While you can not take the mean of a factor variable, you can convert it to a numeric variable, as each of the 3 levels were assigned numeric indices of 1, 2, or 3.

## Convert the Logical Vector

### The logical vector will be converted to:
* A numeric vector, and multiply the random sample by the result
* A factor vector, and multiply the random sample by the result
* A factor vector, and then to a numeric vector, and multiply the random sample by the result

```{r}
as.numeric(pull(Prob1_df, vec_logical))*(pull(Prob1_df, sample))
as.factor(pull(Prob1_df, vec_logical))*(pull(Prob1_df, sample))
as.numeric(as.factor(pull(Prob1_df, vec_logical)))*(pull(Prob1_df, sample))
```

The product of the logical variable, converted to a factor variable, and the random sample did not produce a meaningful result. 


# PROBLEM 2

## Create a Data Frame

```{r}
set.seed(7)

Prob2_df = tibble(
  x = rnorm(500),
  y = rnorm(500),
  vec_log = c(x + y > 1),
  vec_num = as.numeric(vec_log),
  vec_fac = as.factor(vec_log)
)
```

### Vector Description
* There are `r nrow(Prob2_df)` rows and `r ncol(Prob2_df)` columns in the dataset.
* The mean of the sample of x is `r mean(pull(Prob2_df, x))`
* The median of the sample of x is `r median(pull(Prob2_df, x))`
* The standard deviation of the sample of x is `r sd(pull(Prob2_df, x))`
* The proportion of cases for which x + y > 1 is `r sum(pull(Prob2_df, vec_log))/500`

## Make Scatterplots

### Scatterplot: Logical
```{r yx_scatter_logical}
ggplot(Prob2_df, aes(x = x, y = y, color = vec_log)) + geom_point()
```

### Scatterplot: Numeric
```{r yx_scatter_numeric}
ggplot(Prob2_df, aes(x = x, y = y, color = vec_num)) + geom_point()
```

### Scatterplot: Factor
```{r yx_scatter_factor}
ggplot(Prob2_df, aes(x = x, y = y, color = vec_fac)) + geom_point()
```

The scatterplots for the Logical and Factor variables are displayed with a binary color scale, with salmon dots indicating "false" and teal dots indicating "true." The scatterplot for the Numeric variable is displayed with a gradient color scale from 0 to 1, ranging from navy to light blue. This is reflective of the fact that the Numeric variable can take on a range of values between 0 to 1.  

## Export The Logical Scatterplot
```{r yx_scatter_logical_save}
ggsave("yx_scatter_logical.pdf")
```

