---
title: "p8105_hw1_niz2000"
author: "Nora Zakaria"
date: "September 20, 2019"
output: github_document
---

# PROBLEM 1

## Create a Data Frame

```{r}
library (tidyverse)
```

### The data frame consists of:
* A random sample of size 8 from a standard Normal distribution
* A logical vector indicating whether elements of the sample are greater than 0
* A character vector of length 8
* A factor vector of length 8, with 3 different factor levels: "seed", "pit", and "peel"

```{r }
Prob1_df = tibble(
  sample = rnorm(8),
  vec_logical = c(sample > 0), 
  vec_character = c("apple", "banana", "cherry", "date", "elderberry", "fig", "guava", "honeydew"),
  vec_factor = factor(c("seed", "peel", "pit", "pit", "seed", "peel", "seed", "seed")),
)
```

## Mean of Variables in the Data Frame

```{r}
mean(pull(Prob1_df, sample))
mean(pull(Prob1_df, vec_logical))
mean(pull(Prob1_df, vec_character))
mean(pull(Prob1_df, vec_factor))
```

The mean code only displays a result for the mean of the sample and logical vector. It does not display a mean for the character vector or factor vector, as they are not tied to numbers. 

## Convert Variables

```{r eval = FALSE}
as.numeric(pull(Prob1_df, sample))
as.numeric(pull(Prob1_df, vec_logical))
as.numeric(pull(Prob1_df, vec_character))
as.numeric(pull(Prob1_df, vec_factor))
```


# PROBLEM 2