---
title: "p8105_hw1_niz2000"
author: "Nora Zakaria"
date: "2019-09-20 20"
output: github_document
---

# PROBLEM 1

## Create a Data Frame

```{r}
library (tidyverse)
```

### The data frame consists of:
* A random sample of size 8 from a standard Normal distribution
* A logical vector indicating whether elements of the sample are greater than 0
* A character vector of length 8
* A factor vector of length 8, with 3 different factor levels: "seed", "pit", and "peel"

```{r }
set.seed(7)

Prob1_df = tibble(
  sample = rnorm(8),
  vec_logical = c(sample > 0), 
  vec_character = c("apple", "banana", "cherry", "date", "elderberry", "fig", "guava", "honeydew"),
  vec_factor = factor(c("seed", "peel", "pit", "pit", "seed", "peel", "seed", "seed")),
)
```

## Try to Take the Mean of Variables in the Data Frame

```{r}
mean(pull(Prob1_df, sample))
mean(pull(Prob1_df, vec_logical))
mean(pull(Prob1_df, vec_character))
mean(pull(Prob1_df, vec_factor))
```

The mean code only displays a result for the mean of the sample and logical vector. It does not display a mean for the character vector or factor vector, as they are not tied to numbers. 

## Convert Variables

```{r eval = FALSE}
as.numeric(pull(Prob1_df, sample))
as.numeric(pull(Prob1_df, vec_logical))
as.numeric(pull(Prob1_df, vec_character))
as.numeric(pull(Prob1_df, vec_factor))
```

You can only convert the sample, logical vector, and factor vector variables from the data frame to numberic variables. The character variable could not be converted to numeric, as it did not consist of numbers, and did not have assigned numeric indices.

## Convert the Logical Vector

### The logical vector will be converted to:
* A numeric vector, and multiply the random sample by the result
* A factor vector, and multiply the random sample by the result
* A factor vector, and the to a numeric vector, and multiply the random sample by the result

```{r}
as.numeric(pull(Prob1_df, vec_logical))*(pull(Prob1_df, sample))

as.factor(pull(Prob1_df, vec_logical))*(pull(Prob1_df, sample))

as.numeric(as.factor(pull(Prob1_df, vec_logical)))*(pull(Prob1_df, sample))
```


# PROBLEM 2

## Create a Data Frame

```{r}
set.seed(7)

Prob2_df = tibble(
  x = rnorm(500),
  y = rnorm(500),
  vec_log = c(x + y > 1),
  vec_num = c(vec_log),
  vec_fac = c(vec_log)
)
```

## Vector Description
* There are `r nrow(Prob2_df)` rows and `r ncol(Prob2_df)` columns in the dataset.
* The mean of the sample of x is `r mean(pull(Prob2_df, x))`
* The median of the sample of x is `r median(pull(Prob2_df, x))`
* The standard deviation of the sample of x is `r sd(pull(Prob2_df, x))`
* The proportion of cases for which x + y > 1 is `r sum(pull(Prob2_df, vec_log))/500`

## Make Scatterplots

### Scatterplot: Logical
```{r yx_scatter_logical}
ggplot(Prob2_df, aes(x = x, y = y, color = vec_log)) + geom_point()
```

### Scatterplot: Numeric
```{r yx_scatter_numeric}
ggplot(Prob2_df, aes(x = x, y = y, color = vec_num)) + geom_point()
```

### Scatterplot: Factor
```{r yx_scatter_factor}
ggplot(Prob2_df, aes(x = x, y = y, color = vec_fac)) + geom_point()
```